### 2016-07-09 version0.0/intro0.0.tex
finishing intro

\section{Interstellar Medium}
\label{sec: ism_intro}
%how do we observe it
%what the observation tell us
% how do we measure the dust and gas
ISM in galaxies is a complex system with wide range of structures, but this structures can be divided into two main components: Gas and Dust.
Gas in ISM of galaxies is mostly made of hydrogen and helium with 1 per cent of heavier elements (metals), and can be in the forms of clouds or diffuse regions.
Gas clouds contains molecular clouds, cold neutral hydrogen (\hi~) or hot \hi~clouds, and diffuse gas can be either \hii~(ionized hydrogen) regions or hot intercloud mediums.
Dust mostly contains silicate, graphite grains can be seen in dark clouds or galactic cirrus.
%Among these regions in ISM, molecular clouds, \hii~regions and dust clouds have important role in understanding star formation in galaxies. 
Emission lines from atoms or ions (i.e \hii~regions) in a hot gas, lines from molecules in cold clouds and 21~cm emission of \hi~are the main observing signatures of the gas in the ISM of galaxies.
Dust can be observed directly through FIR and sub-mm observation or indirectly through their extinction and attenuation effect (see Sec.~\ref{sec: extinction}).

%%observing \hii region
%what do we observe
%how the line is created
%why it is important for star formation

%%observing molecular clouds
%what do we observe
%how the line is created
%why it is important for star formation

%%observing molecular clouds
%what do we observe
%how the line is created
%why it is important for star formation

%%observingdust
%what do we observe
%how the line is created
%why it is important for star formation

\hii~regions are generally associate with star formation 
%\subsection{Ionized regions}

%\subsection{Molecular clouds}
Molecular clouds in ISM are cold ($\sim10$ K) and dense ($ 50<n<500$ cm$^{-3}$)~\cite{Bolato08}.
These clouds are cold and dense enough to form simple molecules; hence the name, but they are surrounded by cloud of atomic gas~\cite{Kennicutt12}.
The area, where the hydrogen is in a molecular form but the carbon is in atomic state, is called the transition region, dark gas, photo-dissociation regions or photon-dominated regions~\citep[e.g.][]{van88,Hollenbach99}.

%\subsection{Dust}

\subsection{Map of the ISM}
\label{sec: ismmap}
A map of the total gas in the ISM is produced by direct observations of the gas or using interstellar dust as a tracer. 
Neutral and molecular hydrogen are the most common elements in the ISM. Therefore, for producing the map of the total gas in galaxies, maps of these two components can be added together and multiplied by a constant factor to account for heavier elements which are mostly He. Another way to do the mapping is assuming that the ratio of total gas and dust is constant across a galaxy, and convert dust observations to the map of total gas.

@@

\subsubsection*{Molecular Clouds}

 The molecular form of hydrogen in the ISM has no permanent electric dipole moment, which makes it really hard to detect. H$_2$ molecules are located in cool and dense molecular clouds, but fortunately they are not the only component of the molecular gas. The second dominant component, helium, is a mono-atomic gas and has the same problem as hydrogen, but the molecular gas also contains heavier elements such as carbon and oxygen which are combined to form CO \citep{Bolato13}.

CO has a weak permanent electric dipole moment and a ground rotational transition with low excitation energy. Given its low energy and critical density, CO can easily be excited even in cold molecular clouds. Hence CO (usually the $J(1\rightarrow 0)$ rotational transition, observed at 2.6 mm) is used as a tracer of the mass of the molecular cloud dominated by molecular hydrogen \citep[see, for example,][] {Sanders84}. Higher rotational transition of CO can be used as a tracer as well, but they are not as common as the $J(1\rightarrow 0)$.

\cite{Young91} described the relationship between the CO luminosity of a cloud and its mass. The CO luminosity of a cloud is :
\begin{equation}
L_{CO} = D^2 \int I_{CO} d\Omega 
\end{equation}
where D is the distance to the cloud. $I_{CO}$ is the CO brightness temperature integrated over the line profile. It shows in the form of ${\int T_{co} dV}$ where $T_{CO}$ is the peak brightness temperature in CO line and $V$ is the linewidth. For a uniform cloud with a radius $R$, the CO luminosity is given by

@@

 \begin{equation}
 \label{equ: vir}
 M_{cloud} = L_{CO} \sqrt{\frac{4\rho}{3\pi G T_{CO}}}
 \end{equation}
 where $\sqrt{\frac{4\rho}{3\pi G T_{CO}}}$ is called the conversion factor. Equation~\ref{equ: vir} shows that the total mass of molecular clouds and the total CO luminosity of a galaxy are directly related \citep{Young91}. The relation between CO emission and H$_2$ cloud mass is shown as

\begin{equation}
N_{H_2}/\rm cm^{-2} = X_{CO} \times I_{CO}/\rm K km s^{-1}
\end{equation}
where X$_{CO}$ is the conversion factor (also known as the X-factor). The X-factor is different in each galaxy and sometimes is even different in regions within a galaxy due to differences in metallicity, etc. Though assuming constant conversion factor cases such as M82 and M31 can lead to global molecular gas mass estimates that are very accurate,  but in regions with low metallicity there are uncertainties. Different groups are working on the various galaxies to measure the X-factor for each \citep{Wilson95, Bosselli02, Bolato13}.

In order to empirically determine the relation between H$_2$ masses to CO luminosities, many observational attempts have been made in both galactic and extragalactic scales. One of the most significant studies in this regard was \cite{Solomon87} who studied this relation on more than 273 clouds inside the Milky Way and found the strong correlation between Virial mass of clouds and CO luminosity. In the Local Group galaxies, several groups measured the sizes, line widths, and CO luminosities of molecular clouds to investigate the relation between Virial mass and CO luminosity in other environment than the Milky Way. However, extragalactic investigations were limited to nearby galaxies due to technical problems regarding resolution and sensitivity of the telescopes. To measure the clouds in distant galaxies, spatial resolution of maps must be better than 40 pc which is the typical size of a giant molecular cloud.

Pioneering works in measuring the extragalactic conversion factor were done for M31 and M32 \citep[e.g.,][]{Wilson89, Wilson90}. Figure {~\ref{fig: mco}} shows the CO luminosity verses Virial masses of molecular clouds in the Milky Way, M31, M33, and IC10. The extragalactic molecular clouds are similar to those in the Milky Way. The conversion between the CO luminosity and H$_2$ masses is still a controversial topic \citep[e.g.][]{Narayanan11, Bolato13, Sandstrom13}. Problems regarding metallicity are not solved yet and it is still not clear whether the conversion factor is global or local.

\begin{figure}
\label{fig: mco}
\centering
\includegraphics[width=16cm]{../image_intro/mvirial_lco.eps}
\caption{Relation between The Virial mass and CO luminosity for the Milky Way (dots), M33 (open circles), m31 (triangles), and IC 10 (squares) clouds. The Virial masses measured from selected high spatial resolution CO observations are shown. The extragalactic molecular clouds are very similar to those in the Milky Way. Adapted from \cite{Young91}}
\end{figure}

\subsubsection*{Neutral Gas}

Neutral hydrogen clouds are traced by 21-cm emission. The 21-cm emission comes from the fact that most of hydrogen in the ISM (excluding the regions close to type ``O" and ``B" stars) are in their ground state. The electron and proton spins in the ground state can be parallel (i.e. both spin up) or anti-parallel (i.e. proton's spin is up and electron's spin is down or vice versa).

The energy state of anti-parallel mode is slightly less than parallel mode. Hence, electrons in the parallel mode have a tendency to flip to the anti-parallel mode (atoms always want to be in the state with lowest energy possible). Since the energy difference between these two states is small, eventually it takes millions of years before this transition happens. There are large amounts of atomic hydrogen in the ISM. Therefore, at any given time, there are enough hydrogen atoms that are emitting the 21-cm radiation, even though the transition is really rare.

The density of the atomic hydrogen along the line-of-sight is proportional to the intensity of the 21-cm emission. Atomic hydrogens, that are along the line-of-sight contribute to the energy received. These properties make the 21-cm a very useful tool to study gas in the ISM and trace the large-scale distribution of galaxies in the universe (HI is detectable in most spiral galaxies and some elliptical galaxies). Although the 21-cm emission is the most reliable technique to map the ISM, the linear relationship between the intensity and the column density of the gas breaks down when the gas is optically thick \citep{Braun09}.

@@

Studying the gas cloud in the ISM of distant galaxies by using direct methods is almost impossible and not practical. \cite{Hildebran83} was the first person to suggest that one way to estimate the mass of the gas in the ISM might be from the optical depth of the sub-millimetre continuum emission from the dust; continuum dust emission is generally optically thin. The Herschel Space Telescope \cite{Pilbratt10} measured the continuum dust emission from hundreds of galaxies\citep{Eales10, Oliver12}. This amount of observational data provides a unique opportunity to study the ISM of galaxies using dust emission.

 One of the advantages of using the dust emission as a tracer of the gas mass is that unlike the direct method, the high spatial resolution is not necessary anymore. The other important advantage is that this method solves the newly-found problem of the ``dark gas" in the galaxies. Dark gas is a significant fraction of the gas in the galaxy which is traced by neither the 21-cm emission nor the CO emission \citep{Abdo10}. So it is really hard to detect them by telescopes, but accurate gas to dust ratio can lead to an accurate estimate of dark gas mass in galaxies.

There are many disadvantages regarding the use of the gas to dust ratio in the ISM. In order to use the dust as a tracer of the gas mass, first a relationship between the optical depth and the mass of the dust and then a relationship between the mass of the dust and the mass of the gas must be derived. \cite{Draine03} pointed out that this approach is uncertain because of the uncertainly in the radiative efficiency of dust grains. Also methods of measuring the gas to dust ratio in galaxies are not accurate, which means that there are problems in both steps \citep{Hildebran83}. Also by using current telescopes, it is difficult to detect dust emission from galaxies at z $>$ 0.1 \citep{Ealas12}. Besides, in some cases such as the Virgo cluster, dust mass is more tightly correlated with the total gas mass than to the masses of molecular or atomic gas separately \citep{Corbelli11}.

In addition to all the disadvantages mentioned before, the dust method has two major practical problems: firstly, to apply this method, knowing the temperature of the dust is necessary. To solve this problem, measurement of the continuum emission at far-infrared wavelengths enough to cover the peak of the emission must be very accurate \citep{Ealas12}. The other problem is that there is evidence that the gas to dust ratio depends on the metallicity of the gas \citep{Lisenfeld98, Draine07}, but even in direct methods the dependence on metallicity must be solved.

Certainly the gas to dust ratio as a tracer of the total gas in galaxies has a number of problems. Unfortunately, at present, given the available devices and technologies, we cannot reach a high-resolution that is sufficient to detect the gas cloud directly. Therefore, so far this method is the best available solution for measuring the total gas in distant galaxies.

\subsection{Extinction and Attenuation}
\label{sec: extinction}
In this section, dust ``attenuation" and ``extinction" will be introduced and their effects on measuring the SFR will be briefly discussed. More advanced and detailed discussions on this topic is out of the scope of this paper; and for more information one can refer to the review by \citep{Calzetti01}.

Extinction happens when there is a combination of both absorption and scattering of radiation by dust. The distribution of the dust that lies between a source and the observer is irrelevant to the total extinction value because the source is a background point source.

@@

In order to describe the decrease in the intensity of the original beam when it passes through a region where dust particles are present while taking into account the radiation added to the beam by scattering into the line of sight, an integro-differential equation of the radiative transfer of light through dust is used. At UV/optical/near-IR wavelengths, the radiative transfer equation is:

\begin{equation}
\frac{dI_{\nu}}{d\tau} = -I_{\nu}  + \frac{a_{\nu}}{\pi} \int I_{\nu}\phi(\nu,\cos \Theta)d\Omega
\end{equation}
where I$_{\nu}$ is the intensity of radiation, $\tau$ is the dust's optical depth, a$_{\nu}$ is the dust albedo, which refers to the ratio of the scattering coefficient to the sum of the scattering and absorption coefficients. $\phi(\nu,\cos \Theta)$ is the scattering phase function, and $\Theta$ is the angle between the scattered photon and the line of sight. Both a$_{\nu}$ and $\phi(\nu,\cos \Theta)$ are described in more detail in \citep{Draine03}. The source function, i.e., the dust emission, which usually has small values for wavelengths shorter than a few $\mu$m is neglected in the equation above. This decrease in the intensity of the stellar radiation must be calculated and corrected for different emission; otherwise, it causes underestimation of the SFR.

@@

\section{SFR}
\label{sec: sfr_intro}
%beside the normal ones; add SFR based on PAHs, add SFR from SED
Understanding formation of stars leads to understanding galaxy formations. Characterisation of the star formation processes, such as the total SFR and the initial mass function of a galaxy, is necessary in examining its structure formation \citep{McKee07}. The main problem is that measuring the SFR is not trivial and depends on the galaxy morphology, metallicity, IMF, the spatial resolution of a target system, etc. There is a large number of review papers in the literature on how stars form and how their formation is traced. From a theoretical perspective, one can refer to the classic picture of the theory of star formation as reviewed by \cite{Shu87} and more recently by \citep{McKee07}. From an observational standpoint, star formation is discussed by \cite{Kennicutt98b, Kewley02, Bell03, Calzetti07, Calzetti08, Calzetti10, Calzetti13, Kennicutt07, Kennicutt09, Boquien10, Hao11, Kennicutt12}.

Many groups have been trying to define a technique to calibrate emission from the newly-born, hot and massive ``O'' and ``B'' stars to the rate at which stars are being formed. Emission from the young massive stars are normally used as a tracer of the current SFR. Using luminosity of massive stars makes sense if one considers that star formation rate has remained largely constant during the timescale probed by the specific wavelength which is being used as the tracer. The number of massive stars can be used to extrapolate the total number of the high and low mass stars that are formed in a given star-forming region. To do so, the stellar IMF must be known. However, knowing the Stellar IMF is not enough. To have a reliable SFR indicator, the stellar IMF must be fully sampled, which means that in the highest-mass bin at least one star is formed and all other mass bins have one or more stars (see section ~\ref{sec: imf}).

The ``O'' and ``B'' stars can be observed by both using direct and indirect emission from stars; thus the SFR indicators are categorized based on these methods of observation. In the direct method, the SFR indicators can be probed by the ultraviolet (UV), optical, and near-infrared (NIR) emissions, while for probing the stellar light obscured by dust, mid/far-infrared emission is used. The ionizing photons are used in the indirect method. They are emitted by massive stars and traced by the ionized gas \citep[e.g.,][]{Calzetti04, Calzetti07}. In principle, the SFR is traced by the UV emission, the optical light, near-IR and radio wavelengths, hydrogen recombination lines, forbidden metal lines, and also in the sub-millimetre range by using the Bremsstrahlung emission. Moreover, high mass binaries, massive stars and supernova explosions produce X-ray emissions which can be used as a tracer of star formation. Each of these tracers has some systematic errors, and one should decide which of these methods are more precise for a given system. for example using dust IR emission as an indicator is not precise in dwarf galaxies with small amounts of the gas, although still errors from dust extinction and attenuation must be considered (see section ~\ref{sec: ism}).

\subsection{Stellar Initial Mass Function}
\label{sec: imf}
One of the most fundamental and difficult questions that a complete theory of star formation must answer is the initial mass function. In order to determine the SFR from calibrated photometry data, it is necessary to know the IMF. Most problems in modern astrophysical studies regarding the origin and evolution of stars and galaxies can be solved by varying an IMF \citep{Bastin10}. \cite{Salpeter55} empirically derived the IMF from the observed stellar luminosity function of the Solar neighbourhood \citep{Shu87}. He introduced a power-law IMF of the form:

\begin{equation}
\label{equ: salp}
\Phi (\log M) = dN / d \log M \propto M^{-\gamma }
\end{equation} 
where M is the mass of a star, $\gamma$ is the power index, and N is the number of stars in some logarithmic mass range $\log M + d\log M$.

In the late 70s, it was recognised that using the single power-law IMF over all stellar masses is not a correct assumption \citep{Kroupa93, Bastin10}. Since then, many groups have studied the IMF and found different power laws for it (Fig.{~\ref{fig: imf}} ). Most SFR calibrations have the same assumption that the IMF is constant across all environments which is adopted from the standard IMF of \cite{Kroupa01}:

\begin{align}
\chi (M) = dN/dM = A M^{-1.3}    \quad    (0.1 \le M(M{\odot}) \le 0.5)\\                  
           = 0.5 A M^{-2.3}    \quad    (0.5 \le M(M{\odot}) \le 100)
\end{align}
where $\chi(M)$ is the number of stars between masses $M$ and $M+dM$. Although the Salpeter IMF produces more low-mass stars then the Krupa IMF, they produce almost the same number of the high mass stars. Therefore, the SFR calibrations, which mostly trace massive stars in galaxies, based on the Kroupa IMF and Salpeter IMF can be converted to one another by multiplying the calibration's constant by 1.6 \citep{Calzetti13}. \cite{Bastin10} reviewed  the IMF  by using many observational results and showed that the IMF is constant and universal, although there are uncertainties in different mass bins especially at the high mass end.

\begin{figure}[h]
\label{fig: imf}
\centering
\includegraphics[width=16cm]{../image_intro/imf}
\small
\caption{Comparing the IMFs by plotting the mass fraction per dex versus mass that is normalized so that the integral under each curve is unity. The mass ranges from 0.1 to 120 M$_\odot$. Adopted from \cite{Baldry03}}
\end{figure}

>>>>

\section{Interstellar Medium}
\label{sec: ism_intro}
%how do we observe it
%what the observation tell us
% how do we measure the dust and gas
ISM in galaxies is a complex system with wide range of structures, but this structures can be divided into two main components: Gas and Dust.
Gas in ISM of galaxies is mostly made of hydrogen and helium with 1 per cent of heavier elements (metals), and can be in the forms of clouds or diffuse regions.
Gas clouds contains molecular clouds, cold atomic neutral hydrogen (\hi) or hot \hi~clouds, and diffuse gas can be either \hii~(ionized hydrogen) regions or hot intercloud mediums.
Dust mostly contains silicate, graphite grains can be seen in dark clouds or galactic cirrus.
%Among these regions in ISM, molecular clouds, \hii~regions and dust clouds have important role in understanding star formation in galaxies. 
Emission lines from atoms or ions (i.e \hii~regions) in a hot gas, lines from molecules in cold clouds and 21~cm emission of \hi~are the main observing signatures of the gas in the ISM of galaxies.
Dust can be observed directly through FIR and sub-mm observation or indirectly through their extinction and attenuation effect (see Sec.~\ref{sec: extinction}).

Molecular clouds in ISM are cold ($\sim10$ K) and dense ($ 50<n<500$ cm$^{-3}$), masses in molecular clouds range from few to million solar masses. %~\citep{Bolato08}.
Density in the molecular clouds is not uniform; dense and colds clumps.
Since these clumps are ideal places to form stars, studying molecular clouds has an important role in understanding formation of stars
However, H$_2$ molecules, the main component of molecular clouds, have no permanent electric dipole moment which makes them really hard to detect in visible light.
The second dominant component, helium, is a mono-atomic gas and has the same problem as hydrogen, but these clouds also contain heavier elements such as carbon monoxide, hydrogen cyanide, water, ammonia and more than tens of others.
CO molecules take a third place in case of abundance in the molecular clouds.
In fact, most of our knowledge from extragalactic molecular clouds comes from observing emission line of CO molecules, which due to their heavy weight, they have very low rotational state and can be excited in the temperature of molecular clouds. 
Other heavier molecules have emission lines which are detectable in spectrum of clouds (specially galactic ones), but observing CO emission is the most common way to study properties of molecular clouds i.e. their mass (see Sec.~\ref{sec: ismmap} for more details).

The molecular clouds are surrounded by cloud of atomic gas~\citep{Kennicutt12}, which are easily traceable by 21-cm emission.
Hydrogen atoms in the ISM (excluding the regions close to type ``O" and ``B" stars) are in their ground state. 
The electron and proton spins in the ground state can be parallel (i.e. both spin up) or anti-parallel (i.e. proton's spin is up and electron's spin is down or vice versa). 
The energy state of anti-parallel mode is slightly less than parallel mode.
Since atoms always want to be in the state with lowest energy possible, electrons in the parallel mode have a tendency to flip to the anti-parallel mode. 
However, difference between these two states are very small and it takes millions of years before the transition happens.
The large amount of hydrogen atoms, on the other hand, compensate the rareness of the transition and at any given time, there are enough hydrogen atoms to emit the 21-cm radiation. 
The observation of the \hi atoms is specifically necessary for understanding physical properties and dynamics of ISM, which leads to understanding star formation process in ISM~\citep{Walter08}.

\hii~regions are hot and low density regions that are mostly located in the disk of spiral galaxies.
Optically bright \halpha emission from \hii~regions correlates with number of new massive stars in regions and can be used as star formation tracers~\citep[e.g.][]{Kennicutt98b,Calzetti13}. 
High energy UV photon emitted by massive new born stars have sufficient amount of energy to ionize their surrounding gas.
~\halpha emission is main observational feature\hii~regions.
Temperature and density of these regions can be estimated by observing other recombination lines such as H$\beta$, \sii, \oii, \oiii, and \nii from \hii~regions.
Studying \hii~regions provide valuable insight into star forming regions by providing information such as star formation rate, initial mass function (IMF), and distribution of ionizing stellar masses~\citep[][and references therein]{Azimlu11}.

Dust has insignificant effect on mass of ISM, but it plays crucial roles in evolution of ISM.
The total gas mass of galaxies can be determined using optical depth in sub-mm waveband of dust emission. 
In spiral galaxies dust are in cold regions $\sim 30$~K and has power low distribution of size.
Source of dust thermal emission is from stars and shape of the continuum depends on size of the grain.
MIR emission from dust grains are manly dominated by PAHs heated by evolved stellar population~\cite{Smith07a} or recently formed types``A" and ``B'' stars~\cite{Peeters04}.
Large grains that are either heated by light from star forming regions or by interstellar radiation field from total stellar population emit most of their light in FIR~\citep[e.g.][]{Calapa14, lu14}
Dust are main source of extinction and reddening of star lights (See Sec.\ref{sec: extinction} for more information).

\subsection{Map of ISM}
\label{sec: ismmap}
Measuring mass of gas in galaxies is a necessary step to now how much row material is available for forming stars.
A map of total gas mass in ISM is produced by direct observations of gas or using interstellar dust as a tracer. 
Neutral and molecular hydrogen are the most common elements in ISM. 
Therefore, for producing the total gas mass map in galaxies, maps of these two components can be added together and multiplied by a constant factor to account for heavier elements which are mostly He. 
Another way to do the mapping is assuming that the ratio of total gas and dust is constant across the galaxy, and convert dust observations to the map of total gas mass.

@@

%\subsubsection{Molecular Clouds}

CO molecule has a weak permanent electric dipole moment and a ground rotational transition with low excitation energy. 
Given its low energy and critical density, CO can easily be excited even in cold molecular clouds.
Hence CO (usually the $J(1\rightarrow 0)$ rotational transition, observed at 2.6 mm) is used as a tracer of the mass of the molecular cloud dominated by molecular hydrogen~\citep[e.g.][] {Sanders84}.
Higher rotational transition of CO can be used as a tracer as well, but they are not as common as $J(1\rightarrow 0)$.

\cite{Young91} described the relationship between the CO luminosity of a cloud and its mass. The CO luminosity of a cloud is :
\begin{equation}
L_{CO} = D^2 \int I_{CO} d\Omega 
\end{equation}
where D is the distance to the cloud. 
$I_{CO}$ is the CO brightness temperature integrated over the line profile.
It shows in the form of ${\int T_{co} dV}$ where $T_{CO}$ is the peak brightness temperature in CO line and $V$ is the line-width. 
For a uniform cloud with a radius $R$, the CO luminosity is given by

@@

 \begin{equation}
 \label{equ: vir}
 M_{cloud} = L_{CO} \sqrt{\frac{4\rho}{3\pi G T_{CO}}}
 \end{equation}
 where $\sqrt{\frac{4\rho}{3\pi G T_{CO}}}$ is called the conversion factor. 
 Equation~\ref{equ: vir} shows that the total mass of molecular clouds and the total CO luminosity of a galaxy are directly related~\citep{Young91}. 
 The relation between CO emission and H$_2$ cloud mass is shown as

\begin{equation}
N_{H_2}/\rm cm^{-2} = X_{CO} \times I_{CO}/\rm K km s^{-1}
\end{equation}
where X$_{CO}$ is the conversion factor (also known as the X-factor).
The X-factor is different in each galaxy and sometimes is even different in regions within a galaxy due to differences in properties of regions such as metallicity. 
Though assuming constant conversion factor for galaxies like M82 and M31 can lead to accurate estimation of global molecular gas mass, in regions with low metallicity there are uncertainties. 
Various groups are working on observation from different types of galaxies to measure the X-factor for them~\citep{Wilson95, Bosselli02, Bolato13}.

In order to empirically determine the relation between H$_2$ masses and CO luminosities, many observational attempts have been made in both galactic and extragalactic scales. 
One of the most significant studies in this regard had been done by~\cite{Solomon87}, who studied this relation on more than 273 clouds inside the Milky Way and found a strong correlation between Virial mass of molecular clouds and CO luminosity. 
In the Local Group galaxies, several groups measured size, line width, and CO luminosity of molecular clouds and investigate the relation between  their Virial masses and CO emission in environment other than the Milky Way. However, extragalactic investigations were limited to nearby galaxies due to technical problems regarding resolution and sensitivity of the telescopes. 
To measure the clouds in distant galaxies, spatial resolution of maps must be better than 40 pc which is the typical size of a giant molecular cloud~\citep[e.g.][and refrences therein]{Bolato13}.

Pioneering works in measuring the extragalactic conversion factor were done for M31 and M32~\citep[e.g.,][]{Wilson89, Wilson90}. 
Fig.~\ref{fig: mco} shows the CO luminosity verses Virial masses of molecular clouds in the Milky Way, M31, M33, and IC10. 
The extragalactic molecular clouds are similar to those in the Milky Way. 
The conversion between the CO luminosity and H$_2$ masses is still a controversial topic~\citep[e.g.][]{Narayanan11, Bolato13, Sandstrom13}.
Problems regarding metallicity are not solved yet and it is still not clear whether the conversion factor is global or local.

\begin{figure}
\label{fig: mco}
\centering
\includegraphics[width=16cm]{../image_intro/mvirial_lco.eps}
\caption{Relation between The Virial mass and CO luminosity for the Milky Way (dots), M33 (open circles), m31 (triangles), and IC 10 (squares) clouds. The Virial masses measured from selected high spatial resolution CO observations are shown. The extragalactic molecular clouds are very similar to those in the Milky Way. Adapted from~\cite{Young91}}
\end{figure}

%\subsubsection{Neutral Gas}
The density of the atomic hydrogen along the line-of-sight is proportional to the intensity of the 21-cm emission. 
Atomic hydrogens, that are along the line-of-sight contribute to the energy received. 
These properties make the 21-cm a very useful tool to study gas in the ISM and trace the large-scale distribution of galaxies in the universe (\hi is detectable in most spiral galaxies and some elliptical galaxies).
Although the 21-cm emission is the most reliable technique to map the ISM, the linear relationship between the intensity and the column density of the gas breaks down when the gas is optically thick~\citep{Braun09}.

@@

Studying the gas cloud in the ISM of distant galaxies by using direct methods is almost impossible and not practical. 
\cite{Hildebran83} was the first person to suggest that one way to estimate the mass of the gas in the ISM might be from the optical depth of the sub-mm continuum emission from the dust; continuum dust emission is generally optically thin. 
The Herschel Space Telescope \cite{Pilbratt10} measured the continuum dust emission from hundreds of galaxies\citep{Eales10, Oliver12}. 
This amount of observational data provides a unique opportunity to study the ISM of galaxies using dust emission.

One of the advantages of using the dust emission as a tracer of the gas mass is that unlike the direct method, the high spatial resolution is not necessary anymore. 
The other important advantage is that this method solves the newly-found problem of the ``dark gas" in the galaxies. 
Dark gas is a significant fraction of the gas in the galaxy which is traced by neither the 21-cm emission nor the CO emission~\citep{Abdo10}. 
So it is really hard to detect them by telescopes, but accurate gas to dust ratio can lead to an accurate estimate of dark gas mass in galaxies.

There are many disadvantages regarding the use of the gas to dust ratio in the ISM.
In order to use the dust as a tracer of the gas mass, first a relationship between the optical depth and the mass of the dust and then a relationship between the mass of the dust and the mass of the gas must be derived. \cite{Draine03} pointed out that this approach is uncertain because of the uncertainly in the radiative efficiency of dust grains. 
Also methods of measuring the gas to dust ratio in galaxies are not accurate, which means that there are problems in both steps~\citep{Hildebran83}. 
Also by using current telescopes, it is difficult to detect dust emission from galaxies at z $>$ 0.1~\citep{Ealas12}. 
Besides, in some cases such as the Virgo cluster, dust mass is more tightly correlated with the total gas mass than to the masses of molecular or atomic gas separately~\citep{Corbelli11}.

In addition to all the disadvantages mentioned before, the dust method has two major practical problems: firstly, to apply this method, knowing the temperature of the dust is necessary. 
To solve this problem, measurement of the continuum emission at far-infrared wavelengths enough to cover the peak of the emission must be very accurate~\citep{Ealas12}. 
The other problem is that there is evidence that the gas to dust ratio depends on the metallicity of the gas~\citep{Lisenfeld98, Draine07}, but even in direct methods the dependence on metallicity must be solved. 
Certainly the gas to dust ratio as a tracer of the total gas in galaxies has a number of problems. 
Unfortunately, at present, given the available devices and technologies, we cannot reach a high-resolution that is sufficient to detect the gas cloud directly.
Therefore, so far this method is the best available solution for measuring the total gas in distant galaxies.

\subsection{Extinction and Attenuation}
\label{sec: extinction}
In this section, dust ``attenuation" and ``extinction" will be introduced and their effects on measuring the SFR will be briefly discussed.
More advanced and detailed discussions on this topic is out of the scope of this paper; and for more information one can refer to the review by~\citep{Calzetti01}. 
Extinction happens when there is a combination of both absorption and scattering of radiation by dust. The distribution of the dust that lies between a source and the observer is irrelevant to the total extinction value because the source is a background point source.

@@

In order to describe the decrease in the intensity of the original beam when it passes through a region where dust particles are present while taking into account the radiation added to the beam by scattering into the line of sight, an integro-differential equation of the radiative transfer of light through dust is used. 
At UV/optical/near-IR wavelengths, the radiative transfer equation is:
\begin{equation}
\frac{dI_{\nu}}{d\tau} = -I_{\nu}  + \frac{a_{\nu}}{\pi} \int I_{\nu}\phi(\nu,\cos \Theta)d\Omega
\end{equation}
where I$_{\nu}$ is the intensity of radiation, $\tau$ is the dust's optical depth.
a$_{\nu}$ is the dust albedo, which refers to the ratio of the scattering coefficient to the sum of the scattering and absorption coefficients. 
$\phi(\nu,\cos \Theta)$ is the scattering phase function, and $\Theta$ is the angle between the scattered photon and the line of sight. 
Both a$_{\nu}$ and $\phi(\nu,\cos \Theta)$ are described in more detail in~\citep{Draine03}. 
The source function, i.e., the dust emission, which usually has small values for wavelengths shorter than a few $\mu$m is neglected in the equation above. 
This decrease in the intensity of the stellar radiation must be calculated and corrected for different emission; otherwise, it causes underestimation of the SFR.

@@

\section{SFR}
\label{sec: sfr_intro}
Understanding formation of stars leads to understanding galaxies formation and evolution. 
Characterisation of the star formation processes such as SFR and IMF is necessary in examining galaxies structure formation~\citep{McKee07}. 
Measuring the SFR is not trivial and depends on galaxy's morphology, metallicity, IMF, spatial resolution of a target system, and other propertied of galaxies. 
There is a large number of review papers in the literature on how stars form and how their formation is traced. 
From a theoretical perspective, one can refer to the classic picture of the theory of star formation as reviewed by \cite{Shu87} and more recently by~\citep{McKee07}. 
From an observational standpoint, star formation is discussed by \cite[][and references therein]{Kennicutt98b, Kewley02, Calzetti13, Boquien10, Kennicutt12}.

In principle, emission from new stars can be traced by UV emission, optical light, near-IR and radio wavelengths, hydrogen recombination lines, forbidden metal lines, and also in the sub-mm range by using the Bremsstrahlung emission. 
Some of these emission are directly from stars, e.g UV emission, and some are from ISM components around stars that absorb and re-emit light of young stars, e.g FIR emission.
Techniques to calibrate emission from the newly-born stars, preferably hot and massive ones, to the rate at which stars are being formed were subjects of many studies~\citep[e.g.][]{Calzetti07, Kennicutt11, Hao11,Bigiel08} 
Emission from the young massive type ``O'' or ``B'' stars are normally used as a tracer of the current SFR.
One of the main assumptions for using luminosity of massive stars is that SFR has remained largely constant during the timescale probed by the specific wavelength which is being used as the tracer. 
By knowing IMF, the number of massive stars can be used to extrapolate the total number of the high and low mass stars that are formed in a given star-forming region.
To have a reliable SFR indicator, the stellar IMF must be fully sampled to have at least one star in all mass bins (for more detail see Sec.~\ref{sec: imf}).
In general each tracer has some systematic errors, and one should decide which tracer is more accurate for a given system.

\subsection{Stellar Initial Mass Function}
\label{sec: imf}
One of the most fundamental and difficult questions that a complete theory of star formation must answer is what is the stellar (or cores) initial mass distribution of star forming region. 
Since, most of SFR calibrations use emission from specific mass range stars, it is necessary to know the stellar IMF to determine a more accurate SFR from calibrated photometry data. 
Most problems in modern astrophysical studies regarding the origin and evolution of stars and galaxies can be solved by sampling an IMF ~\citep{Bastin10}. 
\cite{Salpeter55} empirically derived stellar IMF from the observed stellar luminosity function of the Solar neighbourhood~\citep{Shu87}. 
He introduced a power-law IMF in the form of:

\begin{equation}
\label{equ: salp}
\Phi (\log M) = dN / d \log M \propto M^{-\gamma }
\end{equation} 
where M is the stellar mass, $\gamma$ is the power index, and $N$ is the number of stars in logarithmic mass range of $\log M + d\log M$.

In the late 70s, it was recognised that using the single power-law IMF over all stellar masses is not a correct assumption and might overestimate number of low-mass stars~\citep{Kroupa93, Bastin10}. 
Since then, many groups have studied the stellar IMFs and found different power-law relations for them (Fig.~\ref{fig: imf} ). 
Most SFR calibrations have the same assumption that the stellar IMF is constant across all environments and adopt it from the standard stellar IMF introduced by\cite{Kroupa01}:
\begin{align}
\chi (M) = dN/dM = A M^{-1.3}    \quad    (0.1 \le M(M{\odot}) \le 0.5)\\                  
           = 0.5 A M^{-2.3}    \quad    (0.5 \le M(M{\odot}) \le 100)
\end{align}
where $\chi(M)$ is the number of stars between masses $M$ and $M+dM$. 
Although the Salpeter IMF produces more low-mass stars than the Krupa IMF, they produce almost the same number of the high-mass stars. 
Therefore, the SFR calibrations, which mostly trace massive stars in galaxies, based on the Kroupa IMF and Salpeter IMF can be converted to one another by multiplying the calibration's constant by 1.6~\citep{Calzetti13}. 
In more recent study,~\cite{Weisz15} used data from the Panchromatic Hubble Andromeda Treasury program~\citep[PHAT][]{Dalcanton12} and showed that for nearby galaxies both Kroupa and Salpeter stellar IMF overestimate amount of stars in all masses.
\cite{Bastin10} reviewed the stellar IMF by using many observational results and showed that the stellar IMF is constant and universal, though there are uncertainties in different mass bins especially at the high mass end.

\begin{figure}
\label{fig: imf}
\centering
\includegraphics[width=16cm]{../image_intro/imf}
\small
\caption{Comparing the IMFs by plotting the mass fraction per dex versus mass that is normalized so that the integral under each curve is unity. The mass ranges from 0.1 to 120 M$_\odot$. Adopted from~\cite{Baldry03}}
\end{figure}
